A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-31 10_applications.tex
TIm: lil fixes

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
\caption{TUD}\label{applications_tud}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
\caption{UM}\label{applications_um}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\begin{subfigure}[t]{.3\figwidth}
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme applied to various example application objects.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
\caption{TUD}\label{applications_tud}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
\caption{UM}\label{applications_um}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\begin{subfigure}[t]{.3\figwidth}
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme applied to various example application objects.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a tilted homogeneous gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}
